---
title: "SocCult"
author: "Tilde Sloth"
date: "2023-04-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading packages
```{r}
pacman::p_load(tidyverse, rjson, jsonlite, dplyr, tidyjson, purrr, plyr, readr, grid, gridExtra, rethinking, lme4, lmerTest, dineq)

```

## Loading data for equal gender ratio (takes 100 years)
```{r}
ER_001 <-list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Equal_ratio/PF_0.01",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

ER_005 <-list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Equal_ratio/PF_0.05",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

ER_01 <- list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Equal_ratio/PF_0.1",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

ER_02 <-list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Equal_ratio/PF_0.2",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

ER_03 <-list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Equal_ratio/PF_0.3",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows
  
ER_04 <-list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Equal_ratio/PF_0.4",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

ER_05 <-list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Equal_ratio/PF_0.5",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows
```

## Loading data for unequal gender ratio (takes 200 years)
```{r}
UR_001 <- list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Unequal_ratio/PF_0.01",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

UR_005 <- list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Unequal_ratio/PF_0.05",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

UR_01 <-list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Unequal_ratio/PF_0.1",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

UR_02 <-list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Unequal_ratio/PF_0.2",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

UR_03 <-list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Unequal_ratio/PF_0.3",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

UR_04 <-list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Unequal_ratio/PF_0.4",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

UR_05 <-list.files(path = "/Users/tildeidunsloth/Desktop/SocCult_exam/data/Unequal_ratio/PF_0.5",
                    pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>% 
  bind_rows

```

## Investigating equal ratio
```{r}
#Equal ratio - perception factor 0.01

ER_001 <- ER_001 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

E001 <- ER_001 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.01")+ theme_bw()

ER_001 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

ER_001%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```


```{r}
#Equal ratio - perception factor 0.05

ER_005 <- ER_005 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

E005 <- ER_005 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.05")+theme_bw()

ER_005 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

ER_005%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```

```{r}
#Equal ratio - perception factor 0.1
ER_01 <- ER_01 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

E1 <-ER_01 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.1")+theme_bw()

ER_01 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

ER_01%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()

```

```{r}
#Equal ratio - perception factor 0.2
ER_02 <- ER_02 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

E2 <- ER_02 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.2")+theme_bw()

ER_02 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

ER_02%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```

```{r}
#Equal ratio - perception factor 0.3
ER_03 <- ER_03 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

E3 <- ER_03 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.3")

ER_03 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

ER_03%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```

```{r}
#Equal ratio - perception factor 0.4
ER_04 <- ER_04 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

E4 <- ER_04 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.4")

ER_04 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

ER_04%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```

```{r}
#Equal ratio - perception factor 0.5
ER_05 <- ER_05 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

E5 <- ER_05 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.5")

ER_05 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

ER_05%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```

## Giant mega plot equal ratio
```{r}
gridExtra::grid.arrange(E001, E005, E1, E2, ncol=2, nrow=2,
     top = textGrob("Equal ratio: Percentage matches relative to swipes",gp=gpar(fontsize=20,font=3)))
```

## Investigating unequal ratio
```{r}
#Unequal ratio - perception factor 0.01

UR_001 <- UR_001 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

U001 <- UR_001 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.01")+theme_bw()

UR_001 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

UR_001%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```


```{r}
#Unequal ratio - perception factor 0.05

UR_005 <- UR_005 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

U005 <- UR_005 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.05")+theme_bw()

UR_005 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

UR_005%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```


```{r}
#Unequal ratio - perception factor 0.1

UR_01 <- UR_01 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

U1 <-UR_01 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.1")+theme_bw()

UR_01 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

UR_01%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```


```{r}
#Unequal ratio - perception factor 0.2

UR_02 <- UR_02 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

U2 <- UR_02 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.2")+theme_bw()

UR_02 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

UR_02%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```

```{r}
#Unequal ratio - perception factor 0.3

UR_03 <- UR_03 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

U3 <- UR_03 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.3")

UR_03 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

UR_03%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```

```{r}
#Unequal ratio - perception factor 0.4

UR_04 <- UR_04 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

U4 <- UR_04 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.4")

UR_04 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

UR_04%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```

```{r}
#Unequal ratio - perception factor 0.5

UR_05 <- UR_05 %>% 
  mutate(Percentage_matches = N_matches/N_swipes * 100, Gender = ifelse(Woman == TRUE, "F", "M"))

U5 <- UR_05 %>% 
  ggplot(aes(x = Percentage_matches, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Perception factor = 0.5")

UR_05 %>% 
  ggplot(aes(x = P_mate_value, fill = Gender)) + geom_density(alpha = 0.5) + ggtitle("Gender differences in perceived mate value")

UR_05%>% 
  ggplot(aes(x = `Mate_value:`, y = Percentage_matches, color = Gender)) + geom_point()
```
## Giant mega plot for unequal ratio
```{r}
gridExtra::grid.arrange(U001, U005, U1, U2, ncol=2, nrow=2,
     top = textGrob("Unequal ratio: Percentage matches relative to swipes",gp=gpar(fontsize=20,font=3)))
```
## Investigating inequality in match acquisition for unequal ratio
```{r}
#H_1.2 (perception_factor = 0.01)
UR_001M <- UR_001 %>% 
  dplyr::filter(Gender == "M")

top_ten_men_U001 <- length(UR_001M$ID)*0.1

data_men_order_U001 <- UR_001M[order(-UR_001M$Percentage_matches),]

number_of_matches_U001 <- sum(UR_001M$N_matches)

data_top_ten_men_U001 <- data_men_order_U001[1:top_ten_men_U001,]

number_of_matches_top_ten_U001 <- sum(data_top_ten_men_U001$N_matches)

TopU001 <- number_of_matches_top_ten_U001/number_of_matches_U001*100
TopU001

# The top 10 % will only get 4 % of all matches
```

```{r}
#H_1.2 (perception_factor = 0.05)
UR_005M <- UR_005 %>% 
  dplyr::filter(Gender == "M")

top_ten_men_U005 <- length(UR_005M$ID)*0.1

data_men_order_U005 <- UR_005M[order(-UR_005M$Percentage_matches),]

number_of_matches_U005 <- sum(UR_005M$N_matches)

data_top_ten_men_U005 <- data_men_order_U005[1:top_ten_men_U005,]

number_of_matches_top_ten_U005 <- sum(data_top_ten_men_U005$N_matches)

TopU005 <- number_of_matches_top_ten_U005/number_of_matches_U005*100

TopU005

# The top 10 % will only get 14.95 % of all matches
```

```{r}
#H_1.2 (perception_factor = 0.1)
UR_01M <- UR_01 %>% 
  dplyr::filter(Gender == "M")

top_ten_men_U01 <- length(UR_01M$ID)*0.1

data_men_order_U01 <- UR_01M[order(-UR_01M$Percentage_matches),]

number_of_matches_U01 <- sum(UR_01M$N_matches)

data_top_ten_men_U01 <- data_men_order_U01[1:top_ten_men_U01,]

number_of_matches_top_ten_U01 <- sum(data_top_ten_men_U01$N_matches)

TopU01 <- number_of_matches_top_ten_U01/number_of_matches_U01*100

TopU01

# The top 10 % will only get 15.8 % of all matches
```

```{r}
#H_1.2 (perception_factor = 0.2)
UR_02M <- UR_02 %>% 
  dplyr::filter(Gender == "M")

top_ten_men_U02 <- length(UR_02M$ID)*0.1

data_men_order_U02 <- UR_02M[order(-UR_02M$Percentage_matches),]

number_of_matches_U02 <- sum(UR_02M$N_matches)

data_top_ten_men_U02 <- data_men_order_U02[1:top_ten_men_U02,]

number_of_matches_top_ten_U02 <- sum(data_top_ten_men_U02$N_matches)

TopU02 <- number_of_matches_top_ten_U02/number_of_matches_U02*100

TopU02

# The top 10 % will only get 16 % of all matches
```

## Investigating inequality in match acquisition for equal ratio
```{r}
#H_1.2 (perception_factor = 0.01)
ER_001M <- ER_001 %>% 
  dplyr::filter(Gender == "M")

top_ten_men_E001 <- length(ER_001M$ID)*0.1

data_men_order_E001 <- ER_001M[order(-ER_001M$Percentage_matches),]

number_of_matches_E001 <- sum(ER_001M$N_matches)

data_top_ten_men_E001 <- data_men_order_E001[1:top_ten_men_E001,]

number_of_matches_top_ten_E001 <- sum(data_top_ten_men_E001$N_matches)

TopE001 <-number_of_matches_top_ten_E001/number_of_matches_E001*100

TopE001

# The top 10 % will only get 3.36 % of all matches
```

```{r}
#H_1.2 (perception_factor = 0.05)
ER_005M <- ER_005 %>% 
  dplyr::filter(Gender == "M")

top_ten_men_E005 <- length(ER_005M$ID)*0.1

data_men_order_E005 <- ER_005M[order(-ER_005M$Percentage_matches),]

number_of_matches_E005 <- sum(ER_005M$N_matches)

data_top_ten_men_E005 <- data_men_order_E005[1:top_ten_men_E005,]

number_of_matches_top_ten_E005 <- sum(data_top_ten_men_E005$N_matches)

TopE005 <-number_of_matches_top_ten_E005/number_of_matches_E005*100

TopE005

# The top 10 % will only get 10 % of all matches
```

```{r}
#H_1.2 (perception_factor = 0.1)
ER_01M <- ER_01 %>% 
  dplyr::filter(Gender == "M")

top_ten_men_E01 <- length(ER_01M$ID)*0.1

data_men_order_E01 <- ER_01M[order(-ER_01M$Percentage_matches),]

number_of_matches_E01 <- sum(ER_01M$N_matches)

data_top_ten_men_E01 <- data_men_order_E01[1:top_ten_men_E01,]

number_of_matches_top_ten_E01 <- sum(data_top_ten_men_E01$N_matches)

TopE01 <-number_of_matches_top_ten_E01/number_of_matches_E01*100

TopE01
# The top 10 % will only get 9.7 % of all matches
```

```{r}
#H_1.2 (perception_factor = 0.2)
ER_02M <- ER_02 %>% 
  dplyr::filter(Gender == "M")

top_ten_men_E02 <- length(ER_02M$ID)*0.1

data_men_order_E02 <- ER_02M[order(-ER_02M$Percentage_matches),]

number_of_matches_E02 <- sum(ER_02M$N_matches)

data_top_ten_men_E02 <- data_men_order_E02[1:top_ten_men_E02,]

number_of_matches_top_ten_E02 <- sum(data_top_ten_men_E02$N_matches)

TopE02 <-number_of_matches_top_ten_E02/number_of_matches_E02*100

TopE02
# The top 10 % will only get 9% of all matches
```

## Combining match acquisition results in a table
```{r}
# creating a table
tab <- matrix(c(TopU001, TopE001, TopU005,TopE005, TopU01, TopE01, TopU02, TopE02), ncol = 2, byrow = TRUE)
colnames(tab) <- c("Unequal Ratio", "Equal Ratio")
rownames(tab) <- c("0.01", "0.05", "0.1", "0.2")
tab <- as.table(tab)
tab
```

## Stat time
```{r}
#Descriptive statistics - linear regression
m_UR_02 <- lmerTest::lmer(Percentage_matches ~ Gender + (1|ID), data = UR_02)
summary(m_UR_02)

m_ER_02 <- lmerTest::lmer(Percentage_matches ~ Gender + (1|ID), ER_02)
summary(m_ER_02)

```

```{r}
#Descriptive statistics - Bayesian binomial regression
UR_02_dat_list <- list(
  N_swipes = UR_02$N_swipes,
  N_matches = UR_02$N_matches,
  Gender = ifelse(UR_02$Gender == "F", 1, 2)
)

m_UR_02_bayes <- ulam(
  alist(N_matches ~ dbinom(N_swipes, p),
        logit(p) <- a[Gender],
        a[Gender] ~ dnorm(0,1.5)
        ), data = UR_02_dat_list, chains = 4)

precis(m_UR_02_bayes, depth = 2)

# computing the difference
post_UR_02 <- extract.samples(m_UR_02_bayes)
mean(inv_logit(post_UR_02$a[,1]))
mean(inv_logit(post_UR_02$a[,2]))

diff_p_UR <- inv_logit(post_UR_02$a[,1]) - inv_logit(post_UR_02$a[,2])
precis(diff_p_UR)


ER_02_dat_list <- list(
  N_swipes = ER_02$N_swipes,
  N_matches = ER_02$N_matches,
  Gender = ifelse(ER_02$Gender == "F", 1, 2)
)

m_ER_02_bayes <- ulam(
  alist(N_matches ~ dbinom(N_swipes, p),
        logit(p) <- a[Gender],
        a[Gender] ~ dnorm(0,1.5)
        ), data = ER_02_dat_list, chains = 4)

precis(m_ER_02_bayes, depth = 2)

# computing the difference
post_ER_02 <- extract.samples(m_ER_02_bayes)

diff_p_ER <- inv_logit(post_ER_02$a[,1]) - inv_logit(post_ER_02$a[,2])
precis(diff_p_ER)
```

## Looking at gini coefficient
```{r}
#Finding gini coefficient
gini.wtd(ER_001$N_matches)
gini.wtd(ER_005$N_matches)
gini.wtd(ER_01$N_matches)
gini.wtd(ER_02$N_matches)

gini.wtd(UR_001$N_matches)
gini.wtd(UR_005$N_matches)
gini.wtd(UR_01$N_matches)
gini.wtd(UR_02$N_matches)

gini.wtd(UR_001M$N_matches)
gini.wtd(UR_005M$N_matches)
gini.wtd(UR_01M$N_matches)
gini.wtd(UR_02M$N_matches)

gini.wtd(ER_001M$N_matches)
gini.wtd(ER_005M$N_matches)
gini.wtd(ER_01M$N_matches)
gini.wtd(ER_02M$N_matches)
```


